An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-10-29 mixedwindow.tex
Update homepage listed on paper and appendix
Remove trailing whitespace characters
Swap some acronyms for predefined macros

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft \protect\url{http://gray.clhn.co}\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 NBER-NSF Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

\begin{abstract} 
  \noindent This paper develops a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
  using a recursive window to estimate the benchmark model but a
  fixed-length rolling window to estimate the alternative. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic, without
  affecting the asymptotic distribution of this test statistic.  The
  paper also presents Monte Carlo evidence that this statistic has
  much higher power than existing out-of-sample statistics in a common
  use-case for these tests: when the DGP is subject to instability.
  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
  and supports their finding that the equity premium is unpredictable
  out-of-sample.

@@

Assumption~\ref{a3} describes the DGP. The weak dependence and moment
conditions are standard. These assumptions are slightly weaker than
similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
because we make use of more recent developments in limit theory, in
particular the CLT for Near-Epoch Dependent (NED) processes proven by
\cite{Jon:97}.

\begin{asmp}\label{a3}%
  The series $y_t$, $x_t$, and $z_t$ are NED of size $-1/2$ on either a
  strong mixing process of size $-\frac{r}{r-2}$ for $r>2$ or a uniform
  mixing process of size $-\frac{r}{2r-2}$ for $r \geq 2$. Moreover,
  $y_t$ and $\yh_{j,t+1}$, $j = 1,\dots,J$, have uniformly bounded $2 r$
  moments.
\end{asmp}

The requirement that the alternative forecasts satisfy a moment
condition, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The functions $\psi_j$ that generate these
forecasts is essentially unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a CLT from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.

>>>>

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft www.econ.iastate.edu/\textasciitilde
    gcalhoun\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 NBER-NSF Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}.}\\%
  Iowa State University}

@@

\begin{abstract}
  \noindent This paper develops a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
  using a recursive window to estimate the benchmark model but a
  fixed-length rolling window to estimate the alternative. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic, without
  affecting the asymptotic distribution of this test statistic.  The
  paper also presents Monte Carlo evidence that this statistic has
  much higher power than existing out-of-sample statistics in a common
  use-case for these tests: when the \dgp\ is subject to instability.
  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
  and supports their finding that the equity premium is unpredictable
  out-of-sample.

@@

Assumption~\ref{a3} describes the \dgp. The weak dependence and moment
conditions are standard. These assumptions are slightly weaker than
similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
because we make use of more recent developments in limit theory, in
particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
\cite{Jon:97}.

\begin{asmp}\label{a3}%
  The series $y_t$, $x_t$, and $z_t$ are \ned\ of size $-1/2$ on either a
  strong mixing process of size $-\frac{r}{r-2}$ for $r>2$ or a uniform
  mixing process of size $-\frac{r}{2r-2}$ for $r \geq 2$. Moreover,
  $y_t$ and $\yh_{j,t+1}$, $j = 1,\dots,J$, have uniformly bounded $2 r$
  moments.
\end{asmp}

The requirement that the alternative forecasts satisfy a moment
condition, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The functions $\psi_j$ that generate these
forecasts is essentially unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.
